\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-12-06 docs/paper/paper.tex
stukje aan PC toegevoegd
meer pseudocode (modified het nuttigst?)

% Needed packages
\documentclass[a4paper, 10pt, english, onecolumn]{article}
\usepackage[english]{babel}
\usepackage[cm]{fullpage}
\usepackage{cite}
\usepackage{anysize}
\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{listings}
\usepackage{hyperref}

\usepackage{amssymb,amsmath}
\usepackage{algorithmicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\newcommand{\keywords}[1]{\par\noindent 
{\bf Keywords\/}. #1}

% Margins & Headers
\marginsize{2.5cm}{2.5cm}{3.0cm}{2.0cm}
\columnsep 0.4in
\footskip 0.4in 
\usepackage{changepage}

@@

\subsection{The PC-algorithm}
\cite{?}
For finding directed edges, the PC-algorithm first finds the undirected structure.
For each two nodes $X$ and $Y$ which are not neighbours in this structure, it also finds a minimal separating set, which is the smallest set acting as a separated set.
This is done by first assuming all nodes are connected, and then testing all pairs of nodes for independence.

@@

>>>>

% Needed packages
\documentclass[a4paper, 10pt, english, onecolumn]{article}
\usepackage[english]{babel}
%\usepackage[cm]{fullpage}
\usepackage{cite}
\usepackage{anysize}
%\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{listings}
\usepackage{hyperref}

\usepackage{amssymb,amsmath}
\usepackage{algorithmicx}
%\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

%\newcommand{\keywords}[1]{\par\noindent 
%{\bf Keywords\/}. #1}

% Margins & Headers
%\marginsize{2.5cm}{2.5cm}{3.0cm}{2.0cm}
%\columnsep 0.4in
%\footskip 0.4in 
%\usepackage{changepage}

@@

\subsection{The PC-algorithm}

\subsection{Informal description}
\cite{?}
For finding directed edges, the PC-algorithm first finds the undirected structure.
For each two nodes $X$ and $Y$ which are not neighbours in this structure, it also finds a minimal separating set, which is the smallest set acting as a separated set.
This is done by first assuming all nodes are connected, and then testing all pairs of nodes for independence.

@@

\subsection{Pseudocode}

The first part of the algorithm finds an undirected graph $G$. For each pair of points which are not connected in this graph, it also finds a separating set:

\begin{algorithmic}
\Function{Structure\_PC}{$data$ used to test independence}
\State connect all pairs of point in undirected graph $G$.
\State $n \gets 0$
\While{there are connected pairs $X$, $Y$ such that $n < |\operatorname{Adjecencies}(X)\setminus\{Y\}| $}
  \ForAll{such connected pairs $X$, $Y$}
    \ForAll{subsets $S$ of $\operatorname{Adjacencies(X)}$ for which $|S| = n$}
      \State test whether $X$ and $Y$ are d-separated given $S$ (Fisher-Z-test on $data$)
      \If{$X$ and $Y$ are d-separated given $S$}
        \State remove the edge $X - Y$ from G
        \State record $S$ as the separating set of $X$ and $Y$
        \State continue with the next pair $X$, $Y$
      \EndIf
    \EndFor
  \EndFor
  n \gets n+1
\EndWhile
\Return G and the separating sets
\EndFunction
\end{algorithmic}

The second part orients edges in this graph $G$ based on the separating sets:

\begin{algorithmic}
\Function{Directional\_PC}{$G$, $sepsets$}
 \State $\text{PDAG} \gets G$
  \ForAll{triples $X$, $Y$, $Z$ with the structure $X - Y - Z$ in $G$ (where $X$ and $Z$ are not connected)}
    \If{$Y$ is not in the separating set of $X$ and $Z$}
      \State Orient $X - Y - Z$ as $X \rightarrow Y \leftarrow Z$ in $\text{PDAG}$
    \EndIf
  \EndFor
  \Repeat
    \ForAll{ordered, connected pairs $X$, $Y$}
      %\If{there is a node $Z$ such that }

      %\EndIf
    \EndFor
  \Until{no more edges are oriented}
\EndFunction
\end{algorithmic}
